Instructions for Typesetting Manuscript\\ Using \LaTeX\footnote{For the title, try not to use more than three lines. Typeset the title in 11 pt Times Roman, boldface, with the first letter of important words capitalized.}

### 2019-10-08 albatros_paper.tex
Add files via upload

\textbf{Bias Tee} - The bias tee is a network made up of 3 ports \footnote{https://www.pasternack.com/bias-tees-category.aspx}. It is used to extract the RF signal from a \SI{100}{m} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{dB/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{m}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}. The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}. It has an insertion loss of 0.16 dB at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\

>>>>

\textbf{Bias Tee} - It is used to extract the RF signal from a \SI{100}{m} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{dB/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{m}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}. The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}. It has an insertion loss of 0.16 dB at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\
